### 2013-12-20 paper/paper.tex
Adding the paper to the repository.

%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\title{Instructions for ACL-2014 Proceedings}

\author{Hao Liu \\
  NYU \\
  {\tt email@domain} \\\And
  Jiali Huang \\
  NYU \\
  {\tt email@domain} \\\And
  Robert Dionne \\
  NYU \\
  {\tt robertsdionne@nyu.edu} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of ACL-2014. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers.  Authors are asked to conform to all the directions
  reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted from the instructions for earlier ACL
proceedings, including those for ACL-2012 by Maggie Li and Michael
White, those from ACL-2010 by Jing-Shing Chang and Philipp Koehn,
those for ACL-2008 by Johanna D. Moore, Simone Teufel, James Allan,
and Sadaoki Furui, those for ACL-2005 by Hwee Tou Ng and Kemal
Oflazer, those for ACL-2002 by Eugene Charniak and Dekang Lin, and
earlier ACL and EACL formats. Those versions were written by several
people, including John Chen, Henry S. Thompson and Donald
Walker. Additional elements were taken from the formatting
instructions of the {\em International Joint Conference on Artificial
  Intelligence}.

\section{Introduction}

The following instructions are directed to authors of papers submitted
to ACL-2014 or accepted for publication in its proceedings. All
authors are required to adhere to these specifications. Authors are
required to provide a Portable Document Format (PDF) version of their
papers. \textbf{The proceedings are designed for printing on A4
  paper.}

Authors from countries in which access to word-processing systems is
limited should contact the publication chairs, Alexander Koller
(\texttt{koller@ling.uni-potsdam.de}) and Yusuke Miyao
(\texttt{yusuke@nii.ac.jp}), as soon as possible.

We will make more detailed instructions available at
\url{http://sites.google.com/site/acl2014publication}. Please check
this website regularly.

\section{General Instructions}

Manuscripts must be in two-column format.  Exceptions to the
two-column format include the title, authors' names and complete
addresses, which must be centered at the top of the first page, and
any full-width figures or tables (see the guidelines in
Subsection~\ref{ssec:first}). {\bf Type single-spaced.}  Start all
pages directly under the top margin. See the guidelines later
regarding formatting the first page.  The manuscript should be
printed single-sided and its length
should not exceed the maximum page limit described in Section~\ref{sec:length}.
Do not number the pages.

\subsection{Electronically-available resources}

We strongly prefer that you prepare your PDF files using \LaTeX\ with
the official ACL 2014 style file (acl2014.sty) and bibliography style
(acl.bst). These files are available at
\url{http://www.cs.jhu.edu/ACL2014/}. You will also find the document
you are currently reading (acl2014.pdf) and its \LaTeX\ source code
(acl2014.tex) on this website.

You can alternatively use Microsoft Word to produce your PDF file. In
this case, we strongly recommend the use of the Word template file
(acl2014.dot) on the ACL 2014 website. If you have an option, we
recommend that you use the \LaTeX2e version. If you will be
  using the Microsoft Word template, we suggest that you anonymize
  your source file so that the pdf produced does not retain your
  identity.  This can be done by removing any personal information
from your source document properties.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). PDF files are usually produced from
\LaTeX\ using the \textit{pdflatex} command. If your version of
\LaTeX\ produces Postscript files, you can convert these into PDF
using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
Adobe Distiller to generate PDF.

Please make sure that your PDF file includes all the necessary fonts
(especially tree diagrams, symbols, and fonts with Asian
characters). When you print or create the PDF file, there is usually
an option in your printer setup to include none, all or just
non-standard fonts.  Please make sure that you select the option of
including ALL the fonts. \textbf{Before sending it, test your PDF by
  printing it from a computer different from the one where it was
  created.} Moreover, some word processors may generate very large PDF
files, where each page is rendered as an image. Such images may
reproduce poorly. In this case, try alternative ways to obtain the
PDF. One way on some systems is to install a driver for a postscript
printer, send your document to the printer specifying ``Output to a
file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm
x 29.7 cm) when formatting the paper. When working with
{\tt dvips}, for instance, one should specify {\tt -t a4}.

Print-outs of the PDF file on A4 paper should be identical to the
hardcopy version. If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chairs as soon as possible.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on A4
paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
 If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's {\bf Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble. If Times Roman is unavailable, use {\bf Computer
  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
  10\% less dense than Adobe's Times Roman font.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|rl|}
\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
document text & 11 pt  &\\
captions & 11 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

\subsection{The First Page}
\label{ssec:first}

Center the title, author's name(s) and affiliation(s) across both
columns. Do not use footnotes for affiliations. Do not include the
paper ID number assigned during the submission process. Use the
two-column format only when you begin the abstract.

{\bf Title}: Place the title centered at the top of the first page, in
a 15-point bold font. (For a complete guide to font sizes and styles,
see Table~\ref{font-table}) Long titles should be typed on two lines
without a blank line intervening. Approximately, put the title at 2.5
cm from the top of the page, followed by a blank line, then the
author's names(s), and the affiliation on the following line. Do not
use only initials for given names (middle initials are allowed). Do
not format surnames in all capitals (e.g., use ``Schlangen'' not
``SCHLANGEN'').  Do not format title and section headings in all
capitals as well except for proper names (such as ``BLEU'') that are
conventionally in all capitals.  The affiliation should contain the
author's complete address, and if possible, an electronic mail
address. Start the body of the first page 7.5 cm from the top of the
page.

The title, author names and addresses should be completely identical
to those entered to the electronical paper submission website in order
to maintain the consistency of author information among all
publications of the conference. If they are different, the publication
chairs may resolve the difference without consulting with you; so it
is in your own interest to double-check that the information is
consistent.

{\bf Abstract}: Type the abstract at the beginning of the first
column. The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.6 cm on each side. Center the word {\bf Abstract} in a 12 point bold
font above the body of the abstract. The abstract should be a concise
summary of the general thesis and conclusions of the paper. It should
be no longer than 200 words. The abstract text should be in 10 point font.

{\bf Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in 
the present document. Do not include page numbers.

{\bf Indent} when starting a new paragraph. Use 11 points for text and 
subsection headings, 12 points for section headings and 15 points for
the title.

\subsection{Sections}

{\bf Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals. Do not number subsubsections.

{\bf Citations}: Citations within the text appear in parentheses
as~\cite{Gusfield:97} or, if the author's name appears in the text
itself, as Gusfield~\shortcite{Gusfield:97}.  Append lowercase letters
to the year in cases of ambiguity.  Treat double authors as
in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
authors are involved. Collapse multiple citations as
in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
as sentence constituents. We suggest that instead of
\begin{quote}
  ``\cite{Gusfield:97} showed that ...''
\end{quote}
you use
\begin{quote}
``Gusfield \shortcite{Gusfield:97}   showed that ...''
\end{quote}

If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
can use the command \verb|\newcite| to get ``author (year)'' citations.

As reviewing will be double-blind, the submitted version of the papers
should not include the authors' names and affiliations. Furthermore,
self-references that reveal the author's identity, e.g.,
\begin{quote}
``We previously showed \cite{Gusfield:97} ...''  
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
``Gusfield \shortcite{Gusfield:97}
previously showed ... ''
\end{quote}

\textbf{Please do not use anonymous citations} and do not include
acknowledgements when submitting your papers. Papers that do not
conform to these requirements may be rejected without review.

\textbf{References}: Gather the full set of references together under
the heading {\bf References}; place the section before any Appendices,
unless they contain references. Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
Provide as complete a citation as possible, using a consistent format,
such as the one for {\em Computational Linguistics\/} or the one in the 
{\em Publication Manual of the American 
Psychological Association\/}~\cite{APA:83}.  Use of full names for
authors rather than initials is preferred.  A list of abbreviations
for common computer science journals can be found in the ACM 
{\em Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations, 
short citations and multiple citations as described above.

{\bf Appendices}: Appendices, if any, directly follow the text and the
references (but see above).  Letter them in sequence and provide an
informative title: {\bf Appendix A. Title of Appendix}.

\subsection{Footnotes}

{\bf Footnotes}: Put footnotes at the bottom of the page and use 9
points text. They may be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the line
separating the footnotes from the text.}

\subsection{Graphics}

{\bf Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns.  Color
illustrations are discouraged, unless you have verified that  
they will be understandable when printed in black ink.

{\bf Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and 
tables below the body, using 11 point text.

\section{XML conversion and supported \LaTeX\ packages}

ACL 2014 innovates over earlier years in that we will attempt to
automatically convert your \LaTeX\ source files to machine-readable
XML with semantic markup. This will facilitate future research that
uses the ACL proceedings themselves as a corpus.

We encourage you to submit a ZIP file of your \LaTeX\ sources along
with the camera-ready version of your paper. We will then convert them
to XML automatically, using the LaTeXML tool
(\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
a number of \LaTeX\ packages, including the ACL 2014 stylefile. These
bindings allow LaTeXML to render the commands from these packages
correctly in XML. For best results, we encourage you to use the
packages that are officially supported by LaTeXML, listed at
\url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms
with appropriate transliterations and/or translations
since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in
the order of: original-form transliteration ``translation''.

\section{Length of Submission}
\label{sec:length}

Long papers may consist of up to 8 pages of content, plus two extra
pages for references. Short papers may consist of up to 4 pages of
content, plus two extra pages for references.  Papers that do not
conform to the specified length and formatting requirements may be
rejected without review.

\section*{Acknowledgments}

The acknowledgments should go immediately before the references.  Do
not number the acknowledgments section. Do not include this section
when submitting your paper for review.

% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2014}

\begin{thebibliography}{}

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

\end{thebibliography}

\end{document}

### 2013-12-20 paper/paper.tex

@@
 
-\title{Instructions for ACL-2014 Proceedings}
+\title{Recursive Neural Network Part-of-Speech Tagger}
 
@@
 \begin{abstract}
-  This document contains the instructions for preparing a camera-ready
-  manuscript for the proceedings of ACL-2014. The document itself
-  conforms to its own specifications, and is therefore an example of
-  what your manuscript should look like. These instructions should be
-  used for both papers submitted for review and for final versions of
-  accepted papers.  Authors are asked to conform to all the directions
-  reported in this document.
+  TODO: Write the abstract
 \end{abstract}
-
-\section{Credits}
-
-This document has been adapted from the instructions for earlier ACL
-proceedings, including those for ACL-2012 by Maggie Li and Michael
-White, those from ACL-2010 by Jing-Shing Chang and Philipp Koehn,
-those for ACL-2008 by Johanna D. Moore, Simone Teufel, James Allan,
-and Sadaoki Furui, those for ACL-2005 by Hwee Tou Ng and Kemal
-Oflazer, those for ACL-2002 by Eugene Charniak and Dekang Lin, and
-earlier ACL and EACL formats. Those versions were written by several
-people, including John Chen, Henry S. Thompson and Donald
-Walker. Additional elements were taken from the formatting
-instructions of the {\em International Joint Conference on Artificial
-  Intelligence}.
 
@@
 
-The following instructions are directed to authors of papers submitted
-to ACL-2014 or accepted for publication in its proceedings. All
-authors are required to adhere to these specifications. Authors are
-required to provide a Portable Document Format (PDF) version of their
-papers. \textbf{The proceedings are designed for printing on A4
-  paper.}
+For our final project, we implemented a recursive neural network part-of-speech tagger based on similar prior work by Socher, Manning and Ng (2010) for building sentence parse trees and work by Collobert and Weston (2011) for their distributed word representations.
+We wanted to explore natural language processing using neural networks, so we chose a small problem (part-of-speech tagging) which we already had experience with during the third homework assignment and applied these modern techniques in neural network research to the problem.
 
-Authors from countries in which access to word-processing systems is
-limited should contact the publication chairs, Alexander Koller
-(\texttt{koller@ling.uni-potsdam.de}) and Yusuke Miyao
-(\texttt{yusuke@nii.ac.jp}), as soon as possible.
+Recursive neural networks are neural network models that allow for cyclic connections between neurons.
 
-We will make more detailed instructions available at
-\url{http://sites.google.com/site/acl2014publication}. Please check
-this website regularly.
+\section{Our Models}
 
-\section{General Instructions}
+TODO: Write about our models.
 
-Manuscripts must be in two-column format.  Exceptions to the
-two-column format include the title, authors' names and complete
-addresses, which must be centered at the top of the first page, and
-any full-width figures or tables (see the guidelines in
-Subsection~\ref{ssec:first}). {\bf Type single-spaced.}  Start all
-pages directly under the top margin. See the guidelines later
-regarding formatting the first page.  The manuscript should be
-printed single-sided and its length
-should not exceed the maximum page limit described in Section~\ref{sec:length}.
-Do not number the pages.
+\subsection{Basic}
 
-\subsection{Electronically-available resources}
+TODO: Describe models.
 
-We strongly prefer that you prepare your PDF files using \LaTeX\ with
-the official ACL 2014 style file (acl2014.sty) and bibliography style
-(acl.bst). These files are available at
-\url{http://www.cs.jhu.edu/ACL2014/}. You will also find the document
-you are currently reading (acl2014.pdf) and its \LaTeX\ source code
-(acl2014.tex) on this website.
+\subsection{Compositional Vector Grammar}
 
-You can alternatively use Microsoft Word to produce your PDF file. In
-this case, we strongly recommend the use of the Word template file
-(acl2014.dot) on the ACL 2014 website. If you have an option, we
-recommend that you use the \LaTeX2e version. If you will be
-  using the Microsoft Word template, we suggest that you anonymize
-  your source file so that the pdf produced does not retain your
-  identity.  This can be done by removing any personal information
-from your source document properties.
+TODO: Describe CVG.
 
-\subsection{Format of Electronic Manuscript}
-\label{sect:pdf}
+\subsection{Future}
 
-For the production of the electronic manuscript you must use Adobe's
-Portable Document Format (PDF). PDF files are usually produced from
-\LaTeX\ using the \textit{pdflatex} command. If your version of
-\LaTeX\ produces Postscript files, you can convert these into PDF
-using \textit{ps2pdf} or \textit{dvipdf}. On Windows, you can also use
-Adobe Distiller to generate PDF.
+TODO: Describe future models.
 
-Please make sure that your PDF file includes all the necessary fonts
-(especially tree diagrams, symbols, and fonts with Asian
-characters). When you print or create the PDF file, there is usually
-an option in your printer setup to include none, all or just
-non-standard fonts.  Please make sure that you select the option of
-including ALL the fonts. \textbf{Before sending it, test your PDF by
-  printing it from a computer different from the one where it was
-  created.} Moreover, some word processors may generate very large PDF
-files, where each page is rendered as an image. Such images may
-reproduce poorly. In this case, try alternative ways to obtain the
-PDF. One way on some systems is to install a driver for a postscript
-printer, send your document to the printer specifying ``Output to a
-file'', then convert the file to PDF.
+\section{Experiments}
 
-It is of utmost importance to specify the \textbf{A4 format} (21 cm
-x 29.7 cm) when formatting the paper. When working with
-{\tt dvips}, for instance, one should specify {\tt -t a4}.
+TODO: Describe experiments.
 
-Print-outs of the PDF file on A4 paper should be identical to the
-hardcopy version. If you cannot meet the above requirements about the
-production of your electronic submission, please contact the
-publication chairs as soon as possible.
+\subsection{Backpropagation Through Time}
 
-\subsection{Layout}
-\label{ssec:layout}
+TODO: Describe back propagation through time.
 
-Format manuscripts two columns to a page, in the manner these
-instructions are formatted. The exact dimensions for a page on A4
-paper are:
+\subsection{Training Tricks}
 
-\begin{itemize}
-\item Left and right margins: 2.5 cm
-\item Top margin: 2.5 cm
-\item Bottom margin: 2.5 cm
-\item Column width: 7.7 cm
-\item Column height: 24.7 cm
-\item Gap between columns: 0.6 cm
-\end{itemize}
+TODO: Describe training tricks.
 
-\noindent Papers should not be submitted on any other paper size.
- If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.
+\subsubsection{Weight Initialization}
 
-\subsection{Fonts}
+TODO: Describe weight initialization.
 
-For reasons of uniformity, Adobe's {\bf Times Roman} font should be
-used. In \LaTeX2e{} this is accomplished by putting
+\subsubsection{AdaGrad}
 
-\begin{quote}
-\begin{verbatim}
-\usepackage{times}
-\usepackage{latexsym}
-\end{verbatim}
-\end{quote}
-in the preamble. If Times Roman is unavailable, use {\bf Computer
-  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
-  10\% less dense than Adobe's Times Roman font.
+TODO: Describe AdaGrad.
 
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{|l|rl|}
-\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
-paper title & 15 pt & bold \\
-author names & 12 pt & bold \\
-author affiliation & 12 pt & \\
-the word ``Abstract'' & 12 pt & bold \\
-section titles & 12 pt & bold \\
-document text & 11 pt  &\\
-captions & 11 pt & \\
-abstract text & 10 pt & \\
-bibliography & 10 pt & \\
-footnotes & 9 pt & \\
-\hline
-\end{tabular}
-\end{center}
-\caption{\label{font-table} Font guide. }
-\end{table}
+\subsection{Analysis}
 
-\subsection{The First Page}
-\label{ssec:first}
+TODO: Describe analysis.
 
-Center the title, author's name(s) and affiliation(s) across both
-columns. Do not use footnotes for affiliations. Do not include the
-paper ID number assigned during the submission process. Use the
-two-column format only when you begin the abstract.
+\subsubsection{Training Progress Diagram}
 
-{\bf Title}: Place the title centered at the top of the first page, in
-a 15-point bold font. (For a complete guide to font sizes and styles,
-see Table~\ref{font-table}) Long titles should be typed on two lines
-without a blank line intervening. Approximately, put the title at 2.5
-cm from the top of the page, followed by a blank line, then the
-author's names(s), and the affiliation on the following line. Do not
-use only initials for given names (middle initials are allowed). Do
-not format surnames in all capitals (e.g., use ``Schlangen'' not
-``SCHLANGEN'').  Do not format title and section headings in all
-capitals as well except for proper names (such as ``BLEU'') that are
-conventionally in all capitals.  The affiliation should contain the
-author's complete address, and if possible, an electronic mail
-address. Start the body of the first page 7.5 cm from the top of the
-page.
+TODO: Describe training progress diagrams.
 
-The title, author names and addresses should be completely identical
-to those entered to the electronical paper submission website in order
-to maintain the consistency of author information among all
-publications of the conference. If they are different, the publication
-chairs may resolve the difference without consulting with you; so it
-is in your own interest to double-check that the information is
-consistent.
+\subsubsection{Comparison to Other Models}
 
-{\bf Abstract}: Type the abstract at the beginning of the first
-column. The width of the abstract text should be smaller than the
-width of the columns for the text in the body of the paper by about
-0.6 cm on each side. Center the word {\bf Abstract} in a 12 point bold
-font above the body of the abstract. The abstract should be a concise
-summary of the general thesis and conclusions of the paper. It should
-be no longer than 200 words. The abstract text should be in 10 point font.
+TODO: Compare to baseline.
 
-{\bf Text}: Begin typing the main body of the text immediately after
-the abstract, observing the two-column format as shown in 
-the present document. Do not include page numbers.
+TODO: Compare to HMM.
 
-{\bf Indent} when starting a new paragraph. Use 11 points for text and 
-subsection headings, 12 points for section headings and 15 points for
-the title.
+\subsubsection{Error Analysis}
 
-\subsection{Sections}
+TODO: Confusion matrices.
 
-{\bf Headings}: Type and label section and subsection headings in the
-style shown on the present document.  Use numbered sections (Arabic
-numerals) in order to facilitate cross references. Number subsections
-with the section number and the subsection number separated by a dot,
-in Arabic numerals. Do not number subsubsections.
+TODO: Histogram for missed tags per sentence.
 
-{\bf Citations}: Citations within the text appear in parentheses
-as~\cite{Gusfield:97} or, if the author's name appears in the text
-itself, as Gusfield~\shortcite{Gusfield:97}.  Append lowercase letters
-to the year in cases of ambiguity.  Treat double authors as
-in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
-authors are involved. Collapse multiple citations as
-in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
-as sentence constituents. We suggest that instead of
-\begin{quote}
-  ``\cite{Gusfield:97} showed that ...''
-\end{quote}
-you use
-\begin{quote}
-``Gusfield \shortcite{Gusfield:97}   showed that ...''
-\end{quote}
+TODO: Histogram for the related position of missed tags in sentence.
 
-If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
-can use the command \verb|\newcite| to get ``author (year)'' citations.
+TODO: Compare to maximum likelihood model.
 
-As reviewing will be double-blind, the submitted version of the papers
-should not include the authors' names and affiliations. Furthermore,
-self-references that reveal the author's identity, e.g.,
-\begin{quote}
-``We previously showed \cite{Gusfield:97} ...''  
-\end{quote}
-should be avoided. Instead, use citations such as 
-\begin{quote}
-``Gusfield \shortcite{Gusfield:97}
-previously showed ... ''
-\end{quote}
+TODO: Specific error examples and hypotheses.
 
-\textbf{Please do not use anonymous citations} and do not include
-acknowledgements when submitting your papers. Papers that do not
-conform to these requirements may be rejected without review.
+TODO: Compare with and without updating word representations.
 
-\textbf{References}: Gather the full set of references together under
-the heading {\bf References}; place the section before any Appendices,
-unless they contain references. Arrange the references alphabetically
-by first author, rather than by order of occurrence in the text.
-Provide as complete a citation as possible, using a consistent format,
-such as the one for {\em Computational Linguistics\/} or the one in the 
-{\em Publication Manual of the American 
-Psychological Association\/}~\cite{APA:83}.  Use of full names for
-authors rather than initials is preferred.  A list of abbreviations
-for common computer science journals can be found in the ACM 
-{\em Computing Reviews\/}~\cite{ACM:83}.
+TODO: Compare larger hidden layer sizes.
 
-The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
-American Psychological Association format, allowing regular citations, 
-short citations and multiple citations as described above.
+\section{Conclusion}
 
-{\bf Appendices}: Appendices, if any, directly follow the text and the
-references (but see above).  Letter them in sequence and provide an
-informative title: {\bf Appendix A. Title of Appendix}.
+\section{Academic Honesty Pledge}
 
-\subsection{Footnotes}
+Honor Pledge
 
-{\bf Footnotes}: Put footnotes at the bottom of the page and use 9
-points text. They may be numbered or referred to by asterisks or other
-symbols.\footnote{This is how a footnote should appear.} Footnotes
-should be separated from the text by a line.\footnote{Note the line
-separating the footnotes from the text.}
-
-\subsection{Graphics}
-
-{\bf Illustrations}: Place figures, tables, and photographs in the
-paper near where they are first discussed, rather than at the end, if
-possible.  Wide illustrations may run across both columns.  Color
-illustrations are discouraged, unless you have verified that  
-they will be understandable when printed in black ink.
-
-{\bf Captions}: Provide a caption for every illustration; number each one
-sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
-Caption of the Table.''  Type the captions of the figures and 
-tables below the body, using 11 point text.
-
-\section{XML conversion and supported \LaTeX\ packages}
-
-ACL 2014 innovates over earlier years in that we will attempt to
-automatically convert your \LaTeX\ source files to machine-readable
-XML with semantic markup. This will facilitate future research that
-uses the ACL proceedings themselves as a corpus.
-
-We encourage you to submit a ZIP file of your \LaTeX\ sources along
-with the camera-ready version of your paper. We will then convert them
-to XML automatically, using the LaTeXML tool
-(\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
-a number of \LaTeX\ packages, including the ACL 2014 stylefile. These
-bindings allow LaTeXML to render the commands from these packages
-correctly in XML. For best results, we encourage you to use the
-packages that are officially supported by LaTeXML, listed at
-\url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}
-
-\section{Translation of non-English Terms}
-
-It is also advised to supplement non-English characters and terms
-with appropriate transliterations and/or translations
-since not all readers understand all such characters and terms.
-Inline transliteration or translation can be represented in
-the order of: original-form transliteration ``translation''.
-
-\section{Length of Submission}
-\label{sec:length}
-
-Long papers may consist of up to 8 pages of content, plus two extra
-pages for references. Short papers may consist of up to 4 pages of
-content, plus two extra pages for references.  Papers that do not
-conform to the specified length and formatting requirements may be
-rejected without review.
-
-\section*{Acknowledgments}
-
-The acknowledgments should go immediately before the references.  Do
-not number the acknowledgments section. Do not include this section
-when submitting your paper for review.
+We pledge our honor that all the work described in this report is solely ours and
+that we have given credit to all third party resources that we have used.
 

### 2013-12-20 paper/paper.tex
Write more introduction.

@@
 \usepackage{latexsym}
+\usepackage{hyperref}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{braket}
 
@@
 
+\subsection{Recursive Neural Networks}
+
 Recursive neural networks are neural network models that allow for cyclic connections between neurons.
+Generally, recursive networks can have very complex structures, but for our application to part-of-speech tagging, we consider a restricted structure in which the network observes its own output on prior sentence context while consuming as input the current word in order to produce a classification label representing the current word's part of speech tag.
+When training the network or using the network to classify an example sentence, we temporarily unroll the recurrent network into an equivalent, feedforward multilayer perceptron with weight matrix shared between all layers.
+
+Our network structure is a simplification of the more general binary tree structure trained by Socher et al.
+(2010) which iteratively constructs a parse tree by evaluating, at the base case, the best combinations of pairs of words, and subsequently the best combinations of pairs of previous combinations.
+Instead, we construct a linear, degenerate tree by always pairing the current word (on the right) to the previous combination (on the left) of prior sentence context and the prior word to obtain a phrase representation.
+We hope that phrase representation captures both the possible parts-of-speech for the current word and distinguishing context that allows an accurate choice of the correct part-of-speech.
+
+\subsection{Distributed Word Representations}
+
+Underlying the entire model are distributed word representations, which we use directly from the research of Collobert and Weston (2011), downloadable from their website (\hyperlink{http://ronan.collobert.com/senna/}{ronan.collobert.com/senna}).
+Distributed word representations are dense vectors embedded within an $n$-dimensional vector space and differ from sparse, ``one-hot" vectors embedded within a $\left\vert\mathcal{V}\right\vert$-dimensional vector space, where $\mathcal{V}$ is the vocabulary of the language domain.
 

### 2013-12-20 paper/paper.tex
Update the paper with more introduction.

@@
 Generally, recursive networks can have very complex structures, but for our application to part-of-speech tagging, we consider a restricted structure in which the network observes its own output on prior sentence context while consuming as input the current word in order to produce a classification label representing the current word's part of speech tag.
-When training the network or using the network to classify an example sentence, we temporarily unroll the recurrent network into an equivalent, feedforward multilayer perceptron with weight matrix shared between all layers.
+When training the network or using the network to classify an example sentence, we temporarily unroll the recurrent network into an equivalent, feedforward multilayer perceptron with the weight matrix shared between all layers.
 
@@
 Instead, we construct a linear, degenerate tree by always pairing the current word (on the right) to the previous combination (on the left) of prior sentence context and the prior word to obtain a phrase representation.
-We hope that phrase representation captures both the possible parts-of-speech for the current word and distinguishing context that allows an accurate choice of the correct part-of-speech.
+We hope that the resulting phrase representation captures both the possible parts-of-speech for the current word and distinguishing context that allows an accurate choice of the correct part-of-speech.
 
@@
 Underlying the entire model are distributed word representations, which we use directly from the research of Collobert and Weston (2011), downloadable from their website (\hyperlink{http://ronan.collobert.com/senna/}{ronan.collobert.com/senna}).
-Distributed word representations are dense vectors embedded within an $n$-dimensional vector space and differ from sparse, ``one-hot" vectors embedded within a $\left\vert\mathcal{V}\right\vert$-dimensional vector space, where $\mathcal{V}$ is the vocabulary of the language domain.
+Distributed word representations are dense vectors embedded within an $n$-dimensional vector space that differ from sparse, ``one-hot" vectors embedded within a $\left\vert\mathcal{V}\right\vert$-dimensional vector space, where $\mathcal{V}$ is the vocabulary of the language domain.
+
+The distributed word representations are induced by training a neural network in an unsupervised manner to distinguish a word within its concrete contexts from randomly chosen replacement words within those same contexts, and then back propagating the errors into an $n\times\left\vert\mathcal{V}\right\vert$-dimensional lookup table with randomly initialized values.
+The lookup table converts between the original ``one-hot" vector representation, which encodes zero information about the word aside from identity, and the superior distributed representation, which encodes a word's contextual information.
+Since we believe a word's context encodes information about that word's part-of-speech, we hypothesize that distributed word representations will be vital to our part-of-speech tagging model.
 

### 2013-12-20 paper/paper.tex
Add all our references.

@@
 
-\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
-Alfred~V. Aho and Jeffrey~D. Ullman.
-\newblock 1972.
-\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
-\newblock Prentice-{Hall}, Englewood Cliffs, NJ.
+\bibitem[\protect\citename{Collobert and Weston}2011]{Collobert:11}
+Ronan~Collobert, Jason~Weston, Léon~Bottou, Michael~Karlen, Koray~Kavukcuoglu and Pavel~Kuksa.
+\newblock 2011.
+\newblock Natural Language Processing (Almost) from Scratch.
+\newblock {\em Journal of Machine Learning Research 12},  (2011) 2461-2505.
+\newblock The MIT Press, Cambridge, MA.
 
-\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
-{American Psychological Association}.
-\newblock 1983.
-\newblock {\em Publications Manual}.
-\newblock American Psychological Association, Washington, DC.
+\bibitem[\protect\citename{Collobert, Kavukcuoglu and Farabet}2011]{Collobert:11}
+Ronan~Collobert, Koray~Kavukcuoglu and Clément~Farabet.
+\newblock 2011.
+\newblock Torch7: A matlab-like environment for machine learning.
+\newblock {\em BigLearn, NIPS Workshop}.
 
-\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
-{Association for Computing Machinery}.
-\newblock 1983.
-\newblock {\em Computing Reviews}, 24(11):503--512.
+\bibitem[\protect\citename{Glorot and Bengio}2010]{Glorot:10}
+Xavier~Glorot and Yoshua~Bengio.
+\newblock 2010.
+\newblock Understanding the difficulty of training deep feedforward neural networks.
+\newblock {\em International Conference on Artificial Intelligence and Statistics}.
 
-\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
-Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
-\newblock 1981.
-\newblock Alternation.
-\newblock {\em Journal of the Association for Computing Machinery},
-  28(1):114--133.
+\bibitem[\protect\citename{Socher, Bauer, Manning and Ng}2013]{Socher:13}
+Richard~Socher, John~Bauer, Christopher~D. Manning and Andrew~Ng.
+\newblock 2013.
+\newblock Parsing with Compositional Vector Grammars.
+\newblock {\em In Proceedings of the ACL conference}.
 
-\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
-Dan Gusfield.
-\newblock 1997.
-\newblock {\em Algorithms on Strings, Trees and Sequences}.
-\newblock Cambridge University Press, Cambridge, UK.
+\bibitem[\protect\citename{Socher, Manning and Ng}2010]{Socher:10}
+Richard~Socher, Christopher~D. Manning and Andrew~Ng.
+\newblock 2010.
+\newblock Learning Continuous Phrase Representations and
+Syntactic Parsing with Recursive Neural Networks.
+\newblock {\em Proceedings of the NIPS-2010 Deep Learning and Unsupervised Feature Learning Workshop}.
 

### 2013-12-20 paper/paper.tex
Add your correct email addresses.

@@
   NYU \\
-  {\tt email@domain} \\\And
+  {\tt haoliu@nyu.edu} \\\And
   Jiali Huang \\
   NYU \\
-  {\tt email@domain} \\\And
+  {\tt jiali.huang@nyu.edu} \\\And
   Robert Dionne \\

### 2013-12-20 paper/paper.tex
Add proper affiliations.

--- 2013-12-20 paper/paper.tex
@@
 \author{Hao Liu \\
-  NYU \\
-  {\tt email@domain} \\\And
+  NYU CIMS \\
+  New York, NY \\
+  {\tt haoliu@nyu.edu} \\\And
   Jiali Huang \\
-  NYU \\
-  {\tt email@domain} \\\And
+  NYU CIMS \\
+  New York, NY \\
+  {\tt jiali.huang@nyu.edu} \\\And
   Robert Dionne \\
-  NYU \\
+  NYU Game Center \\
+  New York, NY \\
   {\tt robertsdionne@nyu.edu} \\}

### 2013-12-20 paper/paper.tex
Fix typo.

@@
 
-The distributed word representations are induced by training a neural network in an unsupervised manner to distinguish a word within its concrete contexts from randomly chosen replacement words within those same contexts, and then back propagating the errors into an $n\times\left\vert\mathcal{V}\right\vert$-dimensional lookup table with randomly initialized values.
+The distributed word representations are induced by training a neural network in an unsupervised manner to distinguish a word within its concrete contexts from randomly chosen replacement words within those same contexts, and then backpropagating the errors into an $n\times\left\vert\mathcal{V}\right\vert$-dimensional lookup table with randomly initialized values.
 The lookup table converts between the original ``one-hot" vector representation, which encodes zero information about the word aside from identity, and the superior distributed representation, which encodes a word's contextual information.

### 2013-12-20 paper/paper.tex
Adding model parameters.

@@
 Underlying the entire model are distributed word representations, which we use directly from the research of Collobert and Weston (2011), downloadable from their website (\hyperlink{http://ronan.collobert.com/senna/}{ronan.collobert.com/senna}).
-Distributed word representations are dense vectors embedded within an $n$-dimensional vector space that differ from sparse, ``one-hot" vectors embedded within a $\left\vert\mathcal{V}\right\vert$-dimensional vector space, where $\mathcal{V}$ is the vocabulary of the language domain.
+Distributed word representations are dense vectors embedded within an $N$-dimensional vector space that differ from sparse, ``one-hot" vectors embedded within a $\left\vert\mathcal{V}\right\vert$-dimensional vector space, where $\mathcal{V}$ is the vocabulary of the language domain.
 
-The distributed word representations are induced by training a neural network in an unsupervised manner to distinguish a word within its concrete contexts from randomly chosen replacement words within those same contexts, and then backpropagating the errors into an $n\times\left\vert\mathcal{V}\right\vert$-dimensional lookup table with randomly initialized values.
+The distributed word representations are induced by training a neural network in an unsupervised manner to distinguish a word within its concrete contexts from randomly chosen replacement words within those same contexts, and then backpropagating the errors into an $N\times\left\vert\mathcal{V}\right\vert$-dimensional lookup table with randomly initialized values.
 The lookup table converts between the original ``one-hot" vector representation, which encodes zero information about the word aside from identity, and the superior distributed representation, which encodes a word's contextual information.
@@
 
-TODO: Write about our models.
+We implemented a recursive neural network with the programming language Lua and the neural network library Torch7 (Collobert, 2011).
+Our code is available on Github at \hyperlink{http://github.com/robertsdionne/nlp}{github.com/robertsdionne/nlp}.
 
-\subsection{Basic}
+The first model we considered was a basic recursive neural network that combines a phrase representation $p_{i-1}$ encompassing words $w_1,w_2,\ldots,w_{i-1}$ and the word representation $w_i$ into an output phrase representation $p_i$ passed to a multilayer perceptron classifier which outputs the guessed tag.
 
-TODO: Describe models.
+The second model we considered was a compositional vector tagger, based upon the compositional vector grammar model by Socher, et al.
+(2013), in which different weight matrices are associated with different part-of-speech tags in order to generate tag-dependent phrase representations, which are then scored instead of classified.
+This model would perform sentence tagging by maximizing the overall score by choosing the correct tag-associated weight matrices for each word using a beam or greedy search.
 
-\subsection{Compositional Vector Grammar}
+The inputs to both models consist of
+
+\centering
+\begin{tabular}{ l r }
+  $\mathcal{V} = \left\{w_1,w_2,\ldots,w_{\left\vert\mathcal{V}\right\vert}\right\}$ & the vocabulary \\
+  $\mathcal{T} = \left\{t_1,t_2,\ldots,t_{\left\vert\mathcal{T}\right\vert}\right\}$ & the part-of-speech tags \\
+  $N = 50$ & the word dimension \\
+  $V\in M_{N\times\left\vert\mathcal{V}\right\vert}(\mathbb{R})$ & the word lookup table \\
+  $\Ket{w_i}\in\mathcal{V}$ & the ``one-hot" vectors \\
+  $V\Ket{w_i}\in\mathbb{R}^N$ & the word vectors \\
+\end{tabular}
+
+\subsection{Basic Recursive Neural Network Model}
+
+\subsection{Compositional Vector Tagger Model}
 
@@
 
-\subsection{Future}
+\subsection{Future Models}
 

### 2013-12-20 paper/paper.tex
Write the description of the RNN model.

@@
 
-The inputs to both models consist of
+The inputs to both models consist of:
 
-\centering
+\begin{center}
 \begin{tabular}{ l r }
@@
   $V\Ket{w_i}\in\mathbb{R}^N$ & the word vectors \\
+  $\Big[\bullet;\bullet\Big]$ & vector concatenation \\
 \end{tabular}
+\end{center}
 
@@
 
+The basic recursive neural network model also has the following parameters:
+
+\begin{center}
+\begin{tabular}{ l r }
+  $W_{combine}\in M_{N\times2N}(\mathbb{R})$ & matrix for combining \\
+  $b_{combine}\in \mathbb{R}^N$ & bias for combining \\
+  $W_{classify}\in M_{\left\vert\mathcal{T}\right\vert\times N}(\mathbb{R})$ & matrix for tagging \\
+  $b_{classify}\in \mathbb{R}^{\left\vert\mathcal{T}\right\vert}$ & bias for tagging \\
+\end{tabular}
+\end{center}
+
+\vspace{5mm}
+We began by training our model on the Penn Treebank sentences from assignment three, available at \hyperlink{http://www.cs.nyu.edu/petrov/restricted/data3.zip}{www.cs.nyu.edu/petrov/restricted/data3.zip}.
+
+To train the model, we first initialize $W_{combine}$, $b_{combine}$, $W_{classify}$ and $b_{classify}$ with small, uniformly distributed random values.
+We will discuss how to choose the range for these values in section \textbf{3.2.1 Weight Initialization} below.
+Then we perform a classification step in which we convert each word into its distributed word representation, pass each of these representations through the unrolled recursive neural network's inputs, and feed the values forward to the classification layers corresponding to each tag output.
+
+For instance, given the sentence $(w_{i_1},w_{i_2},\ldots,w_{i_K})$ of length $K$, we first calculate the word representations $V\Ket{w_{i_1}},\ldots,V\Ket{w_{i_K}}$, then we calculate each phrase representation $p_j$ from the previous phrase representation $p_{j-1}$ and the current word representation $V\Ket{w_{i_j}}$ by concatenating the two representation vectors, multiplying by $W_{combine}$ and adding $b_{combine}$ before applying the $tanh(\cdot)$ function:
+
+$p_j = tanh(W_{combine}\Big[p_{j-1};V\Ket{w_{i_j}}\Big] + b_{combine})$
+
+Finally, each $p_j$ is passed along to the classifier, which applies the operation:
+
+$t_{i_j} = softmax(W_{classify}p_j + b_{classify})$
+
+to obtain the predicted tag $t_{i_j}$ for $w_{i_j}$.
+
+Finally, we perform backpropagation through time, described in section \textbf{3.1} below, to update the weight matrices and bias vectors.
+Performing a backpropagation after classifying each sentence in the dataset performs stochastic gradient descent in minibatches (where we consider one sentence to be a minibatch of tags and words) to update the weight matrices to more accurately predict the golden tags.
+
 \subsection{Compositional Vector Tagger Model}
-
-TODO: Describe CVG.
 

### 2013-12-20 paper/paper.tex
Describe the RNNCVG.

@@
 \end{center}
+\vspace{5mm}
 
@@
 \subsection{Compositional Vector Tagger Model}
+
+The second model we considered uses weight matrices that depend upon the golden tags of the training sentences. The parameters are as follows:
+
+\begin{center}
+\begin{tabular}{ l r }
+  $W_{combine,t}\in M_{N\times2N}(\mathbb{R})$ & matrix for combining tag $t$ \\
+  $b_{combine,t}\in \mathbb{R}^N$ & bias for combining tag $t$ \\
+  $W_{score}\in M_{1\times N}(\mathbb{R})$ & matrix for scoring tags \\
+  $b_{score}\in \mathbb{R}$ & bias for scoring tags \\
+\end{tabular}
+\end{center}
+
+\vspace{5mm}
+The training and classification procedures differ from the basic model.
+First, in unrolling the recurrent neural network, each recurrent layer adopts the weight matrix associated with the golden tag of the word in that position.
+For instance, if $w_{i_3}$ had tag $t_{i_3} = \text{NN}$ then the third recurrent layer would adopt the weight matrix $W_{combine,\text{NN}}$.
+Each recurrent layer adopts the appropriate weight matrix before generating the phrase representations $p_j$.
+We then apply backpropagation to maximize the score for the representations provided by the golden tag weight matrices by updating those matrices and the score matrix.
+
+Raw classification on unlabeled examples now requires a search procedure.
+The brute-force procedure to tag a sentence of length $K$ would be to search through all $K^{\left\vert\mathcal{T}\right\vert}$ sequences of tag weight matrices and return the sequence that attains the highest overall score based on the score matrix.
+As our tag set has size $\left\vert\mathcal{T}\right\vert=48$, this search is intractable for realistic sentences, so a greedy or beam search would need to be used instead.
 

### 2013-12-20 paper/paper.tex
paper work

--- 2013-12-20 paper/paper.tex
@@
 \usepackage{latexsym}
-\usepackage{hyperref}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{braket}
+\usepackage{graphicx}
 
@@
 \author{Hao Liu \\
-  NYU CIMS \\
-  New York, NY \\
-  {\tt haoliu@nyu.edu} \\\And
+  NYU \\
+  {\tt email@domain} \\\And
   Jiali Huang \\
-  NYU CIMS \\
-  New York, NY \\
-  {\tt jiali.huang@nyu.edu} \\\And
+  NYU \\
+  {\tt email@domain} \\\And
   Robert Dionne \\
-  NYU Game Center \\
-  New York, NY \\
+  NYU \\
   {\tt robertsdionne@nyu.edu} \\}
@@
 
-\subsection{Recursive Neural Networks}
-
 Recursive neural networks are neural network models that allow for cyclic connections between neurons.
-Generally, recursive networks can have very complex structures, but for our application to part-of-speech tagging, we consider a restricted structure in which the network observes its own output on prior sentence context while consuming as input the current word in order to produce a classification label representing the current word's part of speech tag.
-When training the network or using the network to classify an example sentence, we temporarily unroll the recurrent network into an equivalent, feedforward multilayer perceptron with the weight matrix shared between all layers.
-
-Our network structure is a simplification of the more general binary tree structure trained by Socher et al.
-(2010) which iteratively constructs a parse tree by evaluating, at the base case, the best combinations of pairs of words, and subsequently the best combinations of pairs of previous combinations.
-Instead, we construct a linear, degenerate tree by always pairing the current word (on the right) to the previous combination (on the left) of prior sentence context and the prior word to obtain a phrase representation.
-We hope that the resulting phrase representation captures both the possible parts-of-speech for the current word and distinguishing context that allows an accurate choice of the correct part-of-speech.
-
-\subsection{Distributed Word Representations}
-
-Underlying the entire model are distributed word representations, which we use directly from the research of Collobert and Weston (2011), downloadable from their website (\hyperlink{http://ronan.collobert.com/senna/}{ronan.collobert.com/senna}).
-Distributed word representations are dense vectors embedded within an $N$-dimensional vector space that differ from sparse, ``one-hot" vectors embedded within a $\left\vert\mathcal{V}\right\vert$-dimensional vector space, where $\mathcal{V}$ is the vocabulary of the language domain.
-
-The distributed word representations are induced by training a neural network in an unsupervised manner to distinguish a word within its concrete contexts from randomly chosen replacement words within those same contexts, and then backpropagating the errors into an $N\times\left\vert\mathcal{V}\right\vert$-dimensional lookup table with randomly initialized values.
-The lookup table converts between the original ``one-hot" vector representation, which encodes zero information about the word aside from identity, and the superior distributed representation, which encodes a word's contextual information.
-Since we believe a word's context encodes information about that word's part-of-speech, we hypothesize that distributed word representations will be vital to our part-of-speech tagging model.
 
@@
 
-We implemented a recursive neural network with the programming language Lua and the neural network library Torch7 (Collobert, 2011).
-Our code is available on Github at \hyperlink{http://github.com/robertsdionne/nlp}{github.com/robertsdionne/nlp}.
+TODO: Write about our models.
 
-The first model we considered was a basic recursive neural network that combines a phrase representation $p_{i-1}$ encompassing words $w_1,w_2,\ldots,w_{i-1}$ and the word representation $w_i$ into an output phrase representation $p_i$ passed to a multilayer perceptron classifier which outputs the guessed tag.
+\subsection{Basic}
 
-The second model we considered was a compositional vector tagger, based upon the compositional vector grammar model by Socher, et al.
-(2013), in which different weight matrices are associated with different part-of-speech tags in order to generate tag-dependent phrase representations, which are then scored instead of classified.
-This model would perform sentence tagging by maximizing the overall score by choosing the correct tag-associated weight matrices for each word using a beam or greedy search.
+TODO: Describe models.
 
-The inputs to both models consist of
-
-\centering
-\begin{tabular}{ l r }
-  $\mathcal{V} = \left\{w_1,w_2,\ldots,w_{\left\vert\mathcal{V}\right\vert}\right\}$ & the vocabulary \\
-  $\mathcal{T} = \left\{t_1,t_2,\ldots,t_{\left\vert\mathcal{T}\right\vert}\right\}$ & the part-of-speech tags \\
-  $N = 50$ & the word dimension \\
-  $V\in M_{N\times\left\vert\mathcal{V}\right\vert}(\mathbb{R})$ & the word lookup table \\
-  $\Ket{w_i}\in\mathcal{V}$ & the ``one-hot" vectors \\
-  $V\Ket{w_i}\in\mathbb{R}^N$ & the word vectors \\
-\end{tabular}
-
-\subsection{Basic Recursive Neural Network Model}
-
-\subsection{Compositional Vector Tagger Model}
+\subsection{Compositional Vector Grammar}
 
@@
 
-\subsection{Future Models}
+\subsection{Future}
 
@@
 
-TODO: Confusion matrices.
+\paragraph{Confusion matrices} 
+We plot the confusion matrix(Figure \ref{Conf_fig}) for the basic RNN model and find that:
+\begin{enumerate}
+\item The \textbf{most serious confusion is between NNP and NN}. This makes sense, because the fact that the embemdings we are using make no difference between captitaled word and noncapitaled word;
+\item  Another strange confusion is from quotes, which was also met in common HMM models. These may come from the overwhelming sequential information;
+\item Other confusions look normal, and also occur in HMM models, like JJ and NN.
+\end{enumerate}
+\begin{figure}
+\includegraphics[scale=0.5]{indomain_conf.png} 
+\includegraphics[scale=0.5]{outdomain_conf.png} 
+\caption{Confusion matrices for basic RNN}\label{Conf_fig}
+\end{figure}
 
-TODO: Histogram for missed tags per sentence.
+\paragraph{Position of wrong tags } 
+We plot the histogram(Figure \ref{Pos_fig}) of related position(absolute positon in sentence divided by sentence length in (0,1] ). 
+\begin{itemize}
+\item \textbf{Indomain}(left figure): The related position is almost uniform distributed.
+\item \textbf{Outdomain}(right figure): The number of wrong tags  is generally increasing upon related position.
+And from different scale of histogram, we find there is a big drop around 0.5( middle of sentece).
+These may come from the sequential similarity between indomain and outdomain.
+These may also come from the limitation of sequential information passing.
+So bi-direct RNN may help.
+\end{itemize}
+\begin{figure}
+\includegraphics[scale=0.25]{indomain_pos.png} 
+\includegraphics[scale=0.25]{outdomain_pos.png} 
+\caption{Histogram of related position of wrong tags, left is in domain, right is out of domain}\label{Pos_fig}
+\end{figure}
 
-TODO: Histogram for the related position of missed tags in sentence.
+\paragraph{Not just maximum likelihood model}
+In the beginning, there is a worry about whether this RNN model can pass and use the sequential information correctly.
+Perhaps, it just learns a maxium likelihood( most frequent ) predictor for each word or even each group of words.
+So we did some experiments to verify the contribution of sequential information in RNN.
 
-TODO: Compare to maximum likelihood model.
+\begin{itemize}
+\item \textbf{Same word test}:  We choose some words with more than one  common tags and see whether our model predict those tags correctly.
+We tested on 'to'( possible tags are TO and IN) and 'work'(common possible tags are NN, VB and VBP).
+RNN predicts 'to' with 0.80 indomain accuracy and 0.77 outdomain, covering TO and IN.
+RNN predicts 'word' with 0.88 indomain accuracy and 0.83 outdomain, covering NN, VB and VBP.
+\item \textbf{Disconnect core module test}: We disconnect the sequential information passing by ignoring the input embeddings from lower layer, and backwarded gradient from upper layer.
+So although it's still a RNN, there is actually no information passed between layers.
+We train this no-seq RNN and original RNN with 100 sentences and 100 iterations, same random seed and training parameters.
+The Figure \ref{Noseq_fig} shows the outdomain accuracy of two models by the number of iterations, which can be also seen from Figure \ref{Leftsize_fig}.
+The difference is not small.
+So we think the sequential information was passed and used at least partially correctly.
+\end{itemize}
+\begin{figure}
+\includegraphics[scale=0.5]{outdomain_noseq.png}
+\caption{Comparision of no-seq RNN and original RNN for disconnect core module test}\label{Noseq_fig}
+\end{figure}
 
-TODO: Specific error examples and hypotheses.
+\paragraph{Different embedding size of state}
+The size of state embeddings(left side of each RNN layer) is another hyper-parameter to set up.
+And it is important because it may determines the importance of previous sequential information comparing to the current word embedding.
+Figure \ref{Leftsize_fig} shows the the outdomain accuracy of two models by the number of iterations.
+And it looks like 20 is around the optimial size for state embeddings.
+\begin{figure}
+	\includegraphics[scale=0.5]{outdomain_leftsize.png}
+	\caption{Outdomain accuracy comparision of different state embedding size} \label{Leftsize_fig}
+\end{figure}
 
@@
 
-TODO: Compare larger hidden layer sizes.
+TODO: Specific error examples and hypotheses.
 
@@
 
-\bibitem[\protect\citename{Collobert and Weston}2011]{Collobert:11}
-Ronan~Collobert, Jason~Weston, Léon~Bottou, Michael~Karlen, Koray~Kavukcuoglu and Pavel~Kuksa.
-\newblock 2011.
-\newblock Natural Language Processing (Almost) from Scratch.
-\newblock {\em Journal of Machine Learning Research 12},  (2011) 2461-2505.
-\newblock The MIT Press, Cambridge, MA.
+\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
+Alfred~V. Aho and Jeffrey~D. Ullman.
+\newblock 1972.
+\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
+\newblock Prentice-{Hall}, Englewood Cliffs, NJ.
 
-\bibitem[\protect\citename{Collobert, Kavukcuoglu and Farabet}2011]{Collobert:11}
-Ronan~Collobert, Koray~Kavukcuoglu and Clément~Farabet.
-\newblock 2011.
-\newblock Torch7: A matlab-like environment for machine learning.
-\newblock {\em BigLearn, NIPS Workshop}.
+\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
+{American Psychological Association}.
+\newblock 1983.
+\newblock {\em Publications Manual}.
+\newblock American Psychological Association, Washington, DC.
 
-\bibitem[\protect\citename{Glorot and Bengio}2010]{Glorot:10}
-Xavier~Glorot and Yoshua~Bengio.
-\newblock 2010.
-\newblock Understanding the difficulty of training deep feedforward neural networks.
-\newblock {\em International Conference on Artificial Intelligence and Statistics}.
+\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
+{Association for Computing Machinery}.
+\newblock 1983.
+\newblock {\em Computing Reviews}, 24(11):503--512.
 
-\bibitem[\protect\citename{Socher, Bauer, Manning and Ng}2013]{Socher:13}
-Richard~Socher, John~Bauer, Christopher~D. Manning and Andrew~Ng.
-\newblock 2013.
-\newblock Parsing with Compositional Vector Grammars.
-\newblock {\em In Proceedings of the ACL conference}.
+\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
+Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
+\newblock 1981.
+\newblock Alternation.
+\newblock {\em Journal of the Association for Computing Machinery},
+  28(1):114--133.
 
-\bibitem[\protect\citename{Socher, Manning and Ng}2010]{Socher:10}
-Richard~Socher, Christopher~D. Manning and Andrew~Ng.
-\newblock 2010.
-\newblock Learning Continuous Phrase Representations and
-Syntactic Parsing with Recursive Neural Networks.
-\newblock {\em Proceedings of the NIPS-2010 Deep Learning and Unsupervised Feature Learning Workshop}.
+\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
+Dan Gusfield.
+\newblock 1997.
+\newblock {\em Algorithms on Strings, Trees and Sequences}.
+\newblock Cambridge University Press, Cambridge, UK.
 

### 2013-12-20 paper/paper.tex

--- 2013-12-20 paper/paper.tex
@@
 \usepackage{latexsym}
+\usepackage{graphicx}
 \usepackage{hyperref}

### 2013-12-20 paper/paper.tex
Save paper.tex in UTF-8 encoding.

@@
 \bibitem[\protect\citename{Collobert and Weston}2011]{Collobert:11}
-Ronan~Collobert, Jason~Weston, Léon~Bottou, Michael~Karlen, Koray~Kavukcuoglu and Pavel~Kuksa.
+Ronan~Collobert, Jason~Weston, Lon~Bottou, Michael~Karlen, Koray~Kavukcuoglu and Pavel~Kuksa.
 \newblock 2011.
@@
 \bibitem[\protect\citename{Collobert, Kavukcuoglu and Farabet}2011]{Collobert:11}
-Ronan~Collobert, Koray~Kavukcuoglu and Clément~Farabet.
+Ronan~Collobert, Koray~Kavukcuoglu and Clment~Farabet.
 \newblock 2011.

### 2013-12-20 paper/paper.tex
empty change
Edit for grammar.

@@
 \paragraph{Confusion matrices} 
-We plot the confusion matrix(Figure \ref{Conf_fig}) for the basic RNN model and find that:
+We plot the confusion matrix (Figure \ref{Conf_fig}) for the basic RNN model and find that:
 \begin{enumerate}
-\item The \textbf{most serious confusion is between NNP and NN}. This makes sense, because the fact that the embemdings we are using make no difference between captitaled word and noncapitaled word;
-\item  Another strange confusion is from quotes, which was also met in common HMM models. These may come from the overwhelming sequential information;
+\item The \textbf{most serious confusion is between NNP and NN}.
+This makes sense because of the fact that the embeddings we are using make no distinction between capitalized and non-capitalized words;
+\item  Another strange confusion is from quotes, which was also met in common HMM models. This may come from the overwhelming sequential information;
 \item Other confusions look normal, and also occur in HMM models, like JJ and NN.
@@
 \paragraph{Position of wrong tags } 
-We plot the histogram(Figure \ref{Pos_fig}) of related position(absolute positon in sentence divided by sentence length in (0,1] ). 
+We plot the histogram (Figure \ref{Pos_fig}) of relative position (absolute position in sentence divided by sentence length in (0, 1]). 
 \begin{itemize}
-\item \textbf{Indomain}(left figure): The related position is almost uniform distributed.
-\item \textbf{Outdomain}(right figure): The number of wrong tags  is generally increasing upon related position.
-And from different scale of histogram, we find there is a big drop around 0.5( middle of sentece).
-These may come from the sequential similarity between indomain and outdomain.
-These may also come from the limitation of sequential information passing.
-So bi-direct RNN may help.
+\item \textbf{In-domain} (left figure): The relative position is almost uniformly distributed.
+\item \textbf{Out-of-domain} (right figure): The number of wrong tags is generally increasing with relative position.
+And from the different scale of this histogram, we find there is a big drop around 0.5 (middle of sentence).
+This may come from the sequential similarity between in-domain and out-of-domain.
+This may also come from the limitation of sequential information passing.
+So a bi-directional RNN may help.
 \end{itemize}
@@
 
-\paragraph{Not just maximum likelihood model}
-In the beginning, there is a worry about whether this RNN model can pass and use the sequential information correctly.
-Perhaps, it just learns a maxium likelihood( most frequent ) predictor for each word or even each group of words.
-So we did some experiments to verify the contribution of sequential information in RNN.
+\paragraph{Not just a maximum likelihood model}
+In the beginning, we worried about whether this RNN model can pass and use the sequential information correctly.
+Perhaps it just learns a maximum likelihood (most frequent) predictor for each word or even each group of words.
+So we did some experiments to verify the contribution of sequential information to the RNN results.
 
 \begin{itemize}
-\item \textbf{Same word test}:  We choose some words with more than one  common tags and see whether our model predict those tags correctly.
-We tested on 'to'( possible tags are TO and IN) and 'work'(common possible tags are NN, VB and VBP).
-RNN predicts 'to' with 0.80 indomain accuracy and 0.77 outdomain, covering TO and IN.
-RNN predicts 'word' with 0.88 indomain accuracy and 0.83 outdomain, covering NN, VB and VBP.
-\item \textbf{Disconnect core module test}: We disconnect the sequential information passing by ignoring the input embeddings from lower layer, and backwarded gradient from upper layer.
-So although it's still a RNN, there is actually no information passed between layers.
-We train this no-seq RNN and original RNN with 100 sentences and 100 iterations, same random seed and training parameters.
-The Figure \ref{Noseq_fig} shows the outdomain accuracy of two models by the number of iterations, which can be also seen from Figure \ref{Leftsize_fig}.
+\item \textbf{Same word test}:  We chose some words with more than one common tag and saw whether our model predicted those tags correctly.
+We tested on `to' (possible tags are TO and IN) and `work' (common possible tags are NN, VB and VBP).
+Our RNN predicts `to' with 0.80 in-domain and 0.77 out-of-domain accuracy, covering TO and IN.
+The RNN predicts `work' with 0.88 in-domain and 0.83 out-of-domain accuracy, covering NN, VB and VBP.
+\item \textbf{Disconnected core module test}: We disconnected the sequential information passing by ignoring the input embeddings from lower layers, and backward gradient from upper layers.
+So although it's still an RNN, there is actually no information passed between layers.
+We trained this non-sequential RNN and the original RNN with 100 sentences and 100 iterations, same random seed and training parameters.
+The Figure \ref{Noseq_fig} shows the out-of-domain accuracy of two models by the number of iterations, which can be also seen from Figure \ref{Leftsize_fig}.
 The difference is not small.
@@
 \includegraphics[scale=0.5]{outdomain_noseq.png}
-\caption{Comparision of no-seq RNN and original RNN for disconnect core module test}\label{Noseq_fig}
+\caption{Comparison of non-sequential RNN and original RNN for disconnected core module test}\label{Noseq_fig}
 \end{figure}
@@
 \paragraph{Different embedding size of state}
-The size of state embeddings(left side of each RNN layer) is another hyper-parameter to set up.
-And it is important because it may determines the importance of previous sequential information comparing to the current word embedding.
-Figure \ref{Leftsize_fig} shows the the outdomain accuracy of two models by the number of iterations.
-And it looks like 20 is around the optimial size for state embeddings.
+The size of state embeddings (left side of each RNN layer) is another hyper-parameter to set up.
+And it is important because it may determine the importance of previous sequential information compared to the current word embedding.
+Figure \ref{Leftsize_fig} shows the the out-of-domain accuracy of two models by the number of iterations.
+And it looks like 20 is around the optimal size for state embeddings.
 \begin{figure}
 	\includegraphics[scale=0.5]{outdomain_leftsize.png}
-	\caption{Outdomain accuracy comparision of different state embedding size} \label{Leftsize_fig}
+	\caption{Out-of-domain accuracy comparison of different state embedding size} \label{Leftsize_fig}
 \end{figure}

### 2013-12-20 paper/paper.tex
Add Fan in fan out tricks.

@@
 \usepackage{braket}
+\usepackage{listings}
 
@@
 
+As the complexity of the compositional vector tagger model is significantly higher than the basic recurrent neural network model, we were unable to properly train the model and implement a satisfactory search procedure within the remaining time of the assignment, so we have omitted analysis of the results of this model.
+
 \subsection{Future Models}
@@
 
-TODO: Describe weight initialization.
+Early on, we randomly initialized our weight matrices and biases using Torch7's uniform tensor function,
+\begin{lstlisting}
+torch.rand(m, n)
+torch.rand(n)
+\end{lstlisting}
+which draws from $\mathcal{U}[0, 1)$ however, we discovered guidelines for weight initialization from \hyperlink{http://deeplearning.net/tutorial/mlp.html\#mlp}{deeplearning.net/tutorial/mlp.html\#mlp}, borrowed from Glorot and Bengio (2010), and decided to explore how they impacted our training convergence.
+
+Glorot and Bengio (2010) analyzed how initial values for weights influenced the early learning of neural networks, specifically those that use $tanh(\cdot)$ or $sigmoid(\cdot)$ and discovered optimal early learning rates with weights drawn from
+\begin{itemize}
+\item $\mathcal{U}\Big[-\sqrt{\frac{6}{fan_{in}+fan_{out}}},\sqrt{\frac{6}{fan_{in}+fan_{out}}}\Big)$ for $tanh$ layers
+\item $\mathcal{U}\Big[-4\sqrt{\frac{6}{fan_{in}+fan_{out}}},4\sqrt{\frac{6}{fan_{in}+fan_{out}}}\Big)$ for $sigmoid$ layers
+\end{itemize}
+where $fan_{in}$ is the number of inputs to the layer and $fan_{out}$ is the number of outputs.
+
+After adopting these new ranges, and initializing our biases to start at zero, our attainable accuracies dramatically increased from the values we presented in our slides, from about $60\%$ to about $80\%$.
 

### 2013-12-21 paper/paper.tex
Adding P parameter for phrase dimension.

@@
   $\mathcal{T} = \left\{t_1,t_2,\ldots,t_{\left\vert\mathcal{T}\right\vert}\right\}$ & the part-of-speech tags \\
-  $N = 50$ & the word dimension \\
+  $N = 50, P = 50$ & word/phrase dimension \\
   $V\in M_{N\times\left\vert\mathcal{V}\right\vert}(\mathbb{R})$ & the word lookup table \\
@@
 \begin{tabular}{ l r }
-  $W_{combine}\in M_{N\times2N}(\mathbb{R})$ & matrix for combining \\
-  $b_{combine}\in \mathbb{R}^N$ & bias for combining \\
-  $W_{classify}\in M_{\left\vert\mathcal{T}\right\vert\times N}(\mathbb{R})$ & matrix for tagging \\
+  $W_{combine}\in M_{P\times(P+N)}(\mathbb{R})$ & matrix for combining \\
+  $b_{combine}\in \mathbb{R}^P$ & bias for combining \\
+  $W_{classify}\in M_{\left\vert\mathcal{T}\right\vert\times P}(\mathbb{R})$ & matrix for tagging \\
   $b_{classify}\in \mathbb{R}^{\left\vert\mathcal{T}\right\vert}$ & bias for tagging \\
@@
 \begin{tabular}{ l r }
-  $W_{combine,t}\in M_{N\times2N}(\mathbb{R})$ & matrix for combining tag $t$ \\
-  $b_{combine,t}\in \mathbb{R}^N$ & bias for combining tag $t$ \\
-  $W_{score}\in M_{1\times N}(\mathbb{R})$ & matrix for scoring tags \\
-  $b_{score}\in \mathbb{R}$ & bias for scoring tags \\
+  $W_{combine,t}\in M_{P\times(P+N)}(\mathbb{R})$ & matrix for tag $t$ \\
+  $b_{combine,t}\in \mathbb{R}^P$ & bias for tag $t$ \\
+  $W_{score}\in M_{1\times P}(\mathbb{R})$ & matrix for scoring \\
+  $b_{score}\in \mathbb{R}$ & bias for scoring \\
 \end{tabular}
@@
 \begin{lstlisting}
-torch.rand(m, n)
-torch.rand(n)
+torch.rand(P, P+N)
+torch.rand(P)
 \end{lstlisting}
@@
 
-After adopting these new ranges, and initializing our biases to start at zero, our attainable accuracies dramatically increased from the values we presented in our slides, from about $60\%$ to about $80\%$.
+After adopting these new ranges, and initializing our biases to start at zero, our attainable accuracies dramatically increased from the values we presented in class in our slides, from about $60\%$ to about $80\%$.
 

### 2013-12-21 paper/paper.tex
Describe experimental setup. Describe training tricks. Fix some transition words.

@@
 
-Finally, each $p_j$ is passed along to the classifier, which applies the operation:
+Subsequently, each $p_j$ is passed along to the classifier, which applies the operation:
 
@@
 
-TODO: Describe experiments.
+Our experiments consisted of training the recursive network on training sentences drawn from the Penn Treebank data of assignment three, as we described above.
+We frequently trained on 100, 1000, 10,000 or 39,815 (all) of the training sentences in exploring the performance of the recursive neural network for part-of-speech tagging.
+Training on the entire data set for 25 iterations, or on 10,000 training sentences for 100 iterations, each took about 4 hours on a 2012 Macbook Pro Retina with a 2.6 GHz Intel Core i7 CPU and 8 GB of RAM.
+
+To evaluate the network, we used a basic metric which counts the ratio of the number of correctly tagged words out of the total number of words within the validation or test set (1700 in-domain validation sentences, 1016 out-of-domain validation sentences and 1015 out-of-domain test sentences).
+We also count the ratio of correctly tagged unknown words, where a word is defined to be unknown if it was not encountered during the training set; however, note that it may be present within $\mathcal{V}$, the vocabulary associated with the distributed representation lookup table.
+If the word is unknown to the distributed representation lookup table, the model falls back upon the distributed representation for the special token ``UNKNOWN."
 
@@
 
-TODO: Describe training tricks.
+Training neural networks can be tricky since the backpropagation algorithm relies upon a learning rate parameter as well as initial weight and bias values.
+The learning rate should not be too large, otherwise the gradient descent will skip over local or global minima.
+However, it should also not be too small, otherwise training may take too long.
+It perhaps should vary over the course of training and decrease in order to better fine tune the fit to the minima.
+However, it's not obvious exactly which set of choices will be best.
+
+We researched existing techniques to choose initial weights and biases, and to better update the weights based on adaptive learning rates, as described in the next subsections.
 

### 2013-12-21 paper/paper.tex
AdaGrad paper

--- 2013-12-21 paper/paper.tex
@@
 \subsubsection{AdaGrad}
+We used the AdaGrad online learning method to train our model.
+Let $\theta$ be a vector of all parameters needed to train in RNN model and $\theta_t$ means the parameter vector before training on $t_{th}$ example.
+And let  $g_{t,i}$ to be the gradient value of $i_{th}$ parameter on $t_{th}$ example.
+Then the AdaGrad is just updating the parameter vector by
+$$\theta_{{t+1},i} = \theta_{{t},i}  - \frac{\alpha}{\sqrt{\sum_{s=1}^t \theta_{{s},i}^2 }} g_{t,i}$$,
+where the $\alpha$ is a constance to set the scale of learning rate.
 
-TODO: Describe AdaGrad.
+We compared the AdaGrad with fixed learning rate online traning.
+The Figure \ref{Adagrad_fig} is the accuarcy curve on training iteration.
+From Figure \ref{Adagrad_fig}, it's quite clear that the AdaGrad converges faster and better than fixed learning rate.
 
+\begin{figure}
+	\includegraphics[scale=0.5]{outdomain_adagrad.png}
+	\includegraphics[scale=0.5]{outdomain_adagrad_unkown.png}
+	\caption{Out-of-domain accuracy  comparison of adaGrad learning rate and fixed learning rate}\label{Adagrad_fig}
+\end{figure}
 \subsection{Analysis}
@@
 This makes sense because of the fact that the embeddings we are using make no distinction between capitalized and non-capitalized words;
-\item  Another strange confusion is from quotes, which was also met in common HMM models. This may come from the overwhelming sequential information;
+\item  Another strange confusion is from quotes, which was also met in common HMM models.
+This may come from the overwhelming sequential information, and it makes big difference on accuracy(about 1\% on out-of-domain accuracy), to keep everything trained automatically;
 \item Other confusions look normal, and also occur in HMM models, like JJ and NN.

### 2013-12-21 paper/paper.tex
paper: overfitting

@@
 \subsubsection{Training Progress Diagram}
-
-TODO: Describe training progress diagrams.
+As we all know, there will be overfitting if we train too "hard" on training set.
+And if overfitting happens, the test accuracy, in our experiments is out-of-domain accuracy, will drop.
+Figure \ref{Adagrad_fig} shows this drop on both total accuracy and unknown word accuracy.
 

### 2013-12-21 paper/paper.tex
Add citation.

@@
 \subsubsection{AdaGrad}
-We used the AdaGrad online learning method to train our model.
-Let $\theta$ be a vector of all parameters needed to train in RNN model and $\theta_t$ means the parameter vector before training on $t_{th}$ example.
-And let  $g_{t,i}$ to be the gradient value of $i_{th}$ parameter on $t_{th}$ example.
+We used the AdaGrad online learning method to train our model (Socher et al., 2013).
+Let $\theta$ be a vector of all parameters needed to train an RNN model and $\theta_t$ means the parameter vector before training on the $t$-th sentence.
+And let  $g_{t,i}$ to be the gradient value of $i_{th}$ parameter on $t$-th sentence.
 Then the AdaGrad is just updating the parameter vector by

### 2013-12-21 paper/paper.tex
Minor fixes.

@@
 For instance, given the sentence $(w_{i_1},w_{i_2},\ldots,w_{i_K})$ of length $K$, we first calculate the word representations $V\Ket{w_{i_1}},\ldots,V\Ket{w_{i_K}}$, then we calculate each phrase representation $p_j$ from the previous phrase representation $p_{j-1}$ and the current word representation $V\Ket{w_{i_j}}$ by concatenating the two representation vectors, multiplying by $W_{combine}$ and adding $b_{combine}$ before applying the $tanh(\cdot)$ function:
-
-$p_j = tanh(W_{combine}\Big[p_{j-1};V\Ket{w_{i_j}}\Big] + b_{combine})$
-
+$$p_j = tanh(W_{combine}\Big[p_{j-1};V\Ket{w_{i_j}}\Big] + b_{combine})$$
 Subsequently, each $p_j$ is passed along to the classifier, which applies the operation:
-
-$t_{i_j} = softmax(W_{classify}p_j + b_{classify})$
-
+$$t_{i_j} = softmax(W_{classify}p_j + b_{classify})$$
 to obtain the predicted tag $t_{i_j}$ for $w_{i_j}$.
@@
 It perhaps should vary over the course of training and decrease in order to better fine tune the fit to the minima.
-However, it's not obvious exactly which set of choices will be best.
+However, it is not obvious exactly which set of choices will be best.
 
@@
 Let $\theta$ be a vector of all parameters needed to train an RNN model and $\theta_t$ means the parameter vector before training on the $t$-th sentence.
-And let  $g_{t,i}$ to be the gradient value of $i_{th}$ parameter on $t$-th sentence.
-Then the AdaGrad is just updating the parameter vector by
+And let $g_{t,i}$ to be the gradient value of $i$-th parameter on the $t$-th sentence.
+Then to perform AdaGrad is just to update the parameter vector by
 $$\theta_{{t+1},i} = \theta_{{t},i}  - \frac{\alpha}{\sqrt{\sum_{s=1}^t \theta_{{s},i}^2 }} g_{t,i}$$,
-where the $\alpha$ is a constance to set the scale of learning rate.
+where the $\alpha$ is a constant to set the scale of the learning rate.
 
-We compared the AdaGrad with fixed learning rate online traning.
-The Figure \ref{Adagrad_fig} is the accuarcy curve on training iteration.
-From Figure \ref{Adagrad_fig}, it's quite clear that the AdaGrad converges faster and better than fixed learning rate.
+We compared the AdaGrad with fixed learning rate online training.
+The Figure \ref{Adagrad_fig} is the accuracy curve on training iteration.
+From Figure \ref{Adagrad_fig}, it is quite clear that the AdaGrad converges faster and better than fixed learning rate.
+The discrepancy between the initial positions is due to plotting after the first iteration over the training set, at which point we've already performed one AdaGrad update for each sentence.
+
+Additionally, we found that performing an AdaGrad update after each word evaluation performed worse than updating once after each sentence evaluation.
 
@@
 \item \textbf{Disconnected core module test}: We disconnected the sequential information passing by ignoring the input embeddings from lower layers, and backward gradient from upper layers.
-So although it's still an RNN, there is actually no information passed between layers.
+So although it is still an RNN, there is actually no information passed between layers.
 We trained this non-sequential RNN and the original RNN with 100 sentences and 100 iterations, same random seed and training parameters.

### 2013-12-21 paper/paper.tex
Add argmax.

@@
 \usepackage{listings}
+
+\newcommand{\argmax}{\operatornamewithlimits{argmax}}
 
@@
 Subsequently, each $p_j$ is passed along to the classifier, which applies the operation:
-$$t_{i_j} = softmax(W_{classify}p_j + b_{classify})$$
+$$t_{i_j} = \argmax\limits_{t} softmax(W_{classify}p_j + b_{classify})$$
 to obtain the predicted tag $t_{i_j}$ for $w_{i_j}$.

### 2013-12-21 paper/paper.tex
Add two figures and one citation. Describe back propagation through time.

@@
 
+\begin{figure}
+	\includegraphics[scale=0.3]{model_figure.png}
+	\caption{Recursive Neural Network Model}\label{Model_fig}
+\end{figure}
+
 \subsection{Compositional Vector Tagger Model}
@@
 
-TODO: Describe back propagation through time.
+Backpropagation through time is a technique to run backpropagation against recursive neural networks, which include cyclic connections.
+We perform backpropagation through time automatically by running standard backpropagation against our unrolled recursive neural network with shared weight matrices.
+Each gradient update to the weight matrix is independently accumulated, resulting in the correct overall update.
+We perform the gradient update in minibatches, where a single sentence is a mini batch of tagged words and we simultaneously accumulate the errors for each of the words as we backpropogate.
+See Figure \ref{Bptt_fig} (Mikolov, 2012).
+
+\begin{figure}
+	\includegraphics[scale=0.5]{bptt.png}
+	\caption{Back Propagation Through Time (Mikolov, 2012)}\label{Bptt_fig}
+\end{figure}
 
@@
 
+\bibitem[\protect\citename{Mikolov}2012]{Mikolov:12}
+Tomáš~Mikolov.
+\newblock 2012.
+\newblock Statistical Language Models Based on Neural Networks.
+\newblock {\em Diss. Ph. D. thesis, Brno University of Technology}.
+
 \bibitem[\protect\citename{Socher, Bauer, Manning and Ng}2013]{Socher:13}

### 2013-12-21 paper/paper.tex
Remove whitespace.

@@
 Each gradient update to the weight matrix is independently accumulated, resulting in the correct overall update.
-We perform the gradient update in minibatches, where a single sentence is a mini batch of tagged words and we simultaneously accumulate the errors for each of the words as we backpropogate.
+We perform the gradient update in minibatches, where a single sentence is a minibatch of tagged words and we simultaneously accumulate the errors for each of the words as we backpropogate.
 See Figure \ref{Bptt_fig} (Mikolov, 2012).

### 2013-12-21 paper/paper.tex
Revise grammar.
paper: future models

--- 2013-12-21 paper/paper.tex
@@
 \usepackage{listings}
-
-\newcommand{\argmax}{\operatornamewithlimits{argmax}}
 
@@
 For instance, given the sentence $(w_{i_1},w_{i_2},\ldots,w_{i_K})$ of length $K$, we first calculate the word representations $V\Ket{w_{i_1}},\ldots,V\Ket{w_{i_K}}$, then we calculate each phrase representation $p_j$ from the previous phrase representation $p_{j-1}$ and the current word representation $V\Ket{w_{i_j}}$ by concatenating the two representation vectors, multiplying by $W_{combine}$ and adding $b_{combine}$ before applying the $tanh(\cdot)$ function:
-$$p_j = tanh(W_{combine}\Big[p_{j-1};V\Ket{w_{i_j}}\Big] + b_{combine})$$
+
+$p_j = tanh(W_{combine}\Big[p_{j-1};V\Ket{w_{i_j}}\Big] + b_{combine})$
+
 Subsequently, each $p_j$ is passed along to the classifier, which applies the operation:
-$$t_{i_j} = \argmax\limits_{t} softmax(W_{classify}p_j + b_{classify})$$
+
+$t_{i_j} = softmax(W_{classify}p_j + b_{classify})$
+
 to obtain the predicted tag $t_{i_j}$ for $w_{i_j}$.
@@
 
-TODO: Describe future models.
+\paragraph{Bi-direction Recursive Neural Network}
+From Section~\ref{sec:confm} Figure \ref{Pos_fig}, we find it's more likely to make mistakes on the end of sentence.
+It makes sense, because our basic RNN model uses only forward sequential information.
+So we think bi-direction model will help, at least on basic RNN.
+As for CVG model, which is simulating the HMM model considering the tags of whole sentence together, bi-direction model may also help to kind of simulate CRF.
+There are two bi-direction models we are thinking:
+\begin{itemize}
+\item \textbf{Independent training and combine the probability: } Train two RNN models, and tagging the sentence by combining the predicted probability from two models' classifier part( after the softmax ).
+\item \textbf{Jointly training: } Train two RNN models jointly, and concaten two phrase representations and pass it to a shared classifier, which will in turn backward the gradients to two model.
+So that the classifier part will get the forward and backward sequential information from two phrase representations.
+Figure~\ref{fig:bi-direc} shows the idea of this jointly training model.
+\end{itemize}
+\begin{figure}
+\includegraphics[scale=0.5]{bi_direct.png}
+\caption{Idea chart for jointly training bi-direction RNN model}\label{fig:bi-direc}
+\end{figure}
+
+\paragraph{Complex combination and classify model}
+We are using one layer linear neural network on both combination and classify parts, because it's easy to train.
+In the beginning, we did try two layer neural network, but it's too slow to train( about 5 times slower) and add another two hyper parameter to set by human.
+However because the higher ability to capture more complex pattern, complex combination and classify may have better performance.
+Especially on classify part, we can use any machine learning classification model that can backward gradients.
+
+\paragraph{Update lookup table}
+In the begining, we tried to update the lookup table together with other parameters.
+But the result is much worse than not update.
+But because deep learning people do update the feature learning layers(in our model is just lookup table), so it's reasonable to try this.
+And instead updating at the beginning of training, we can begin the updating after other parameters are well trained.
 
@@
 It perhaps should vary over the course of training and decrease in order to better fine tune the fit to the minima.
-However, it is not obvious exactly which set of choices will be best.
+However, it's not obvious exactly which set of choices will be best.
 
@@
 \subsubsection{AdaGrad}
-We used the AdaGrad online learning method to train our model (Socher et al., 2013).
-Let $\theta$ be a vector of all parameters needed to train an RNN model and $\theta_t$ means the parameter vector before training on the $t$-th sentence.
-And let $g_{t,i}$ to be the gradient value of $i$-th parameter on the $t$-th sentence.
-Then to perform AdaGrad is just to update the parameter vector by
+We used the AdaGrad online learning method to train our model.
+Let $\theta$ be a vector of all parameters needed to train in RNN model and $\theta_t$ means the parameter vector before training on $t_{th}$ example.
+And let  $g_{t,i}$ to be the gradient value of $i_{th}$ parameter on $t_{th}$ example.
+Then the AdaGrad is just updating the parameter vector by
 $$\theta_{{t+1},i} = \theta_{{t},i}  - \frac{\alpha}{\sqrt{\sum_{s=1}^t \theta_{{s},i}^2 }} g_{t,i}$$,
-where the $\alpha$ is a constant to set the scale of the learning rate.
+where the $\alpha$ is a constance to set the scale of learning rate.
 
-We compared the AdaGrad with fixed learning rate online training.
-The Figure \ref{Adagrad_fig} is the accuracy curve on training iteration.
-From Figure \ref{Adagrad_fig}, it is quite clear that the AdaGrad converges faster and better than fixed learning rate.
-The discrepancy between the initial positions is due to plotting after the first iteration over the training set, at which point we've already performed one AdaGrad update for each sentence.
-
-Additionally, we found that performing an AdaGrad update after each word evaluation performed worse than updating once after each sentence evaluation.
+We compared the AdaGrad with fixed learning rate online traning.
+The Figure \ref{Adagrad_fig} is the accuarcy curve on training iteration.
+From Figure \ref{Adagrad_fig}, it's quite clear that the AdaGrad converges faster and better than fixed learning rate.
 
@@
 
-\subsubsection{Error Analysis}
+\subsubsection{Error Analysis}  \label{sec:confm}
 
@@
 \item \textbf{Disconnected core module test}: We disconnected the sequential information passing by ignoring the input embeddings from lower layers, and backward gradient from upper layers.
-So although it is still an RNN, there is actually no information passed between layers.
+So although it's still an RNN, there is actually no information passed between layers.
 We trained this non-sequential RNN and the original RNN with 100 sentences and 100 iterations, same random seed and training parameters.
@@
 
-TODO: Compare with and without updating word representations.
-
 TODO: Specific error examples and hypotheses.
@@
 \section{Conclusion}
+
+\section{Future Works}
 

### 2013-12-21 paper/paper.tex

--- 2013-12-21 paper/paper.tex
@@
 
-TODO: Describe analysis.
-
 \subsubsection{Training Progress Diagram}
 As we all know, there will be overfitting if we train too "hard" on training set.
-And if overfitting happens, the test accuracy, in our experiments is out-of-domain accuracy, will drop.
+And if overfitting happens, the test accuracy (in our experiments, the out-of-domain accuracy) will drop.
 Figure \ref{Adagrad_fig} shows this drop on both total accuracy and unknown word accuracy.

### 2013-12-21 paper/paper.tex
Add a reference.
Add revisions plus the results table in the Analysis section.

--- 2013-12-21 paper/paper.tex
@@
 To train the model, we first initialize $W_{combine}$, $b_{combine}$, $W_{classify}$ and $b_{classify}$ with small, uniformly distributed random values.
-We will discuss how to choose the range for these values in section \textbf{3.2.1 Weight Initialization} below.
+We will discuss how to choose the range for these values in Section \ref{Weights} below.
 Then we perform a classification step in which we convert each word into its distributed word representation, pass each of these representations through the unrolled recursive neural network's inputs, and feed the values forward to the classification layers corresponding to each tag output.
@@
 
-TODO: Describe future models.
+\paragraph{Bi-directional Recursive Neural Network}
+From Section~\ref{sec:confm} Figure \ref{Pos_fig}, we find it is more likely to make mistakes on the end of sentences.
+It makes sense, because our basic RNN model uses only forward sequential information.
+So we think a bi-directional model will help, at least compared to the basic RNN.
+As for CVG model, which is simulating the HMM model considering the tags of whole sentence together, a bi-directional model may also help to kind of simulate CRF.
+There are two bi-direction models we are thinking:
+\begin{itemize}
+\item \textbf{Independently training and combining the probability: } Train two RNN models, and tag the sentence by combining the predicted probability from the two models' classifiers (after the softmax).
+\item \textbf{Jointly training: } Train two RNN models jointly, and concatenate two phrase representations and pass it to a shared classifier, which will in turn backward propagate the gradients to the two models so that the classifier part will get the forward and backward sequential information from two phrase representations.
+Figure~\ref{fig:bi-direc} shows the idea of this jointly training model.
+\end{itemize}
+\begin{figure}
+\includegraphics[scale=0.5]{bi_direct.png}
+\caption{Idea chart for jointly training bi-direction RNN model}\label{fig:bi-direc}
+\end{figure}
+
+\paragraph{Complex combination and classification model}
+We are using one layer linear neural network on both combination and classification parts, because it is easy to train.
+In the beginning, we did try a two layer neural network, but it was too slow to train (about five times slower) and added another two hyper parameters to choose.
+However, because of the higher ability to capture more complex patterns, complex combination and classification may have better performance.
+Especially on classification part, we can use any machine learning classification model that can backward propagate gradients.
+
+\paragraph{Update the lookup table}
+In the beginning, we tried to update the lookup table together with other parameters.
+But the result was much worse than not updating it.
+But because deep learning researchers do update the feature learning layers (in our model, just lookup table), it is reasonable to try this.
+And instead of updating at the beginning of training, we can begin the updating after other parameters are well trained.
 
@@
 
-\subsubsection{Weight Initialization}
+\subsubsection{Weight Initialization}\label{Weights}
 
@@
 \end{lstlisting}
-which draws from $\mathcal{U}[0, 1)$ however, we discovered guidelines for weight initialization from \hyperlink{http://deeplearning.net/tutorial/mlp.html\#mlp}{deeplearning.net/tutorial/mlp.html\#mlp}, borrowed from Glorot and Bengio (2010), and decided to explore how they impacted our training convergence.
+which draws from $\mathcal{U}[0, 1)$.
+However, we discovered guidelines for weight initialization from \hyperlink{http://deeplearning.net/tutorial/mlp.html\#mlp}{deeplearning.net/tutorial/mlp.html\#mlp}, borrowed from Glorot and Bengio (2010), and decided to explore how they impacted our training convergence.
 
@@
 
-TODO: Compare to baseline.
+Below, we tally the results against the in-domain validation dataset and the out-of-domain validation dataset on all significantly performing recursive neural network models compared to the hidden-markov-model+TNT, plain hidden-markov-model and maximum likelihood tag models.
 
-TODO: Compare to HMM.
+The AdaGrad variants started with a learning rate parameter at 0.1.
+The non-AdaGrad variants started with a learning rate of 0.0005.
+The RNN models trained on the entire training set (39815 sentences) were trained for 25 iterations.
+The RNN models trained on just 10,000 sentences were trained for 100 iterations.
 
-\subsubsection{Error Analysis}
+Because we stripped all capitalization from our training and test data before converting words to their distributed vector representations, we noticed a high error rate due to conflating proper nouns with regular nouns, so to be fair to our model we evaluated the best model with no distinction between the two tags NNP and NN to see how it would fare had it properly considered capitalization as a feature.
+
+\begin{center}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{ l | ll | ll }
+  Model & In & (In Unk) & Out & (Out Unk) \\
+  \hline
+  HMM+TNT & 95.88 & (87.13) & 93.67 & (84.61) \\
+  RNN$_{39815}$ NN=NNP & 94.52 & (88.39) & 91.70 & (83.21) \\
+  HMM & 95.52 & (63.95) & 91.23 & (53.00) \\
+  AdaGrad RNN$_{39815}$ & 93.58 & (76.90) & 90.41 & (69.82) \\
+  RNN$_{39815}$ & 93.47 & (77.06) & 90.28 & (70.43) \\
+  AdaGrad RNN$_{10,000}$ & 93.02 & (79.17) & 90.12 & (73.43) \\
+  RNN$_{10,000}$ & 92.72 & (77.51) & 89.54 & (69.60) \\
+  Max Likelihood Tag & 91.31 & (42.74) & 87.01 & (53.31) \\
+\end{tabular}%
+}
+\end{center}
+
+\subsubsection{Error Analysis}  \label{sec:confm}
 

### 2013-12-21 paper/paper.tex
paper: abstract

--- 2013-12-21 paper/paper.tex
@@
 \begin{abstract}
-  TODO: Write the abstract
+ We use recursive neural network (RNN) on part of speech task (POS).
+There are two models are proposed and implemented, basic RNN and Compositional Vector Tagger(CVT) RNN.
+The performance of basic RNN is close to the HMM model and with high probability beat it if captialization information is captured.
+The forever tagging time of CVT model we do not analysis.
+We tried some very useful neural network training trics and detailly analysis the performance of basic RNN, such as verifying the contribution of sequential information and error rates of different parts of sentence and so on.
 \end{abstract}
@@
 
-\subsection{Future Models}
+\subsection{Future Models}\label{sec:futuremodel}
 
@@
 And instead updating at the beginning of training, we can begin the updating after other parameters are well trained.
+
+\paragraph{Rerank with CVG}
+When we implemented and tested CVG model, the forever tagging time for each sentence stopped us from working with it.
+So in the future, we can use the rerank idea from Socher's SVG paper.
+Basically, we get top N, say 100, tagging candidates from other models, and use CVG model to get score for each sentence and rerank the candidates by these scores.
 
@@
 
-TODO: Specific error examples and hypotheses.
-
 \section{Conclusion}
@@
 \section{Future Works}
+Because the limited time of final projects, there are still a lot of things we want to do in the future.
+We mentioned some new models to try in Section \ref{sec:futuremodel}, and here are some most wanted works to do:
+\begin{itemize}
+\item Training and tagging the CVG model: we have mentioned the hardness of training and tagging with CVG model.
+In the future, we want to training a CVG model no matter how long it may takes, say several days or weeks.
+And implement the rerank trick mentioned  in Section \ref{sec:futuremodel}.
+\item Move to GPU: We are working with torch (http://www.torch.ch), which is made by NYU people and supports GPU.
+So in the future, we can use GPU to speed up both traning and tagging.
+And Theano(http://deeplearning.net/software/theano/) can another choice, which has python interface and also GPU supporting and has very good neural networks supporting.
+\end{itemize}
 

### 2013-12-21 paper/paper.tex

--- 2013-12-21 paper/paper.tex
@@
 And instead of updating at the beginning of training, we can begin the updating after other parameters are well trained.
+
+\paragraph{Rerank with CVG}
+When we implemented and tested CVG model, the forever tagging time for each sentence stopped us from working with it.
+So in the future, we can use the rerank idea from Socher's SVG paper.
+Basically, we get top N, say 100, tagging candidates from other models, and use CVG model to get score for each sentence and rerank the candidates by these scores.
 

### 2013-12-21 paper/paper.tex
Add a sentence.

--- 2013-12-21 paper/paper.tex
@@
 Figure \ref{Leftsize_fig} shows the the out-of-domain accuracy of two models by the number of iterations.
-And it looks like 20 is around the optimal size for state embeddings.
+And it looks like 20 is around the optimal size for state embeddings given a training set size of 100.
+However, we trained on the full training set and observed better performance at the original state embedding size of 50.
 \begin{figure}
@@
 \end{figure}
-
-TODO: Specific error examples and hypotheses.
 

### 2013-12-21 paper/paper.tex
Revisions and s/CVG/CVT/

--- 2013-12-21 paper/paper.tex
@@
 \begin{abstract}
- We use recursive neural network (RNN) on part of speech task (POS).
+We use a recursive neural network (RNN) on part-of-speech tagging task (POS).
 There are two models are proposed and implemented, basic RNN and Compositional Vector Tagger(CVT) RNN.
@@
 So we think a bi-directional model will help, at least compared to the basic RNN.
-As for CVG model, which is simulating the HMM model considering the tags of whole sentence together, a bi-directional model may also help to kind of simulate CRF.
+As for CVT model, which is simulating the HMM model considering the tags of whole sentence together, a bi-directional model may also help to kind of simulate CRF.
 There are two bi-direction models we are thinking:
@@
 
-\paragraph{Rerank with CVG}
-When we implemented and tested CVG model, the forever tagging time for each sentence stopped us from working with it.
-So in the future, we can use the rerank idea from Socher's SVG paper.
-Basically, we get top N, say 100, tagging candidates from other models, and use CVG model to get score for each sentence and rerank the candidates by these scores.
+\paragraph{Rerank with CVT}
+When we implemented and tested the CVT model, the forever tagging time for each sentence stopped us from working with it.
+So in the future, we can use the rerank idea from Socher's CVG paper.
+Basically, we get top N, say 100, tagging candidates from other models, and use CVT model to get score for each sentence and rerank the candidates by these scores.
 
@@
 \begin{itemize}
-\item Training and tagging the CVG model: we have mentioned the hardness of training and tagging with CVG model.
-In the future, we want to training a CVG model no matter how long it may takes, say several days or weeks.
+\item Training and tagging the CVT model: we have mentioned the hardness of training and tagging with CVT model.
+In the future, we want to training a CVT model no matter how long it may takes, say several days or weeks.
 And implement the rerank trick mentioned  in Section \ref{sec:futuremodel}.

### 2013-12-21 paper/paper.tex
Revise abstract.

@@
 \begin{abstract}
-We use a recursive neural network (RNN) on part-of-speech tagging task (POS).
-There are two models are proposed and implemented, basic RNN and Compositional Vector Tagger(CVT) RNN.
-The performance of basic RNN is close to the HMM model and with high probability beat it if captialization information is captured.
-The forever tagging time of CVT model we do not analysis.
-We tried some very useful neural network training trics and detailly analysis the performance of basic RNN, such as verifying the contribution of sequential information and error rates of different parts of sentence and so on.
+We use a recursive neural network (RNN) on a part-of-speech tagging task (POS).
+We propose and implement two models: a basic RNN and a Compositional Vector Tagger (CVT) RNN.
+The performance of the basic RNN is close to the HMM model and with high probability will beat it if capitalization information is captured.
+The intractable tagging time of the CVT model means we cannot analyze it.
+We tried some useful neural network training tricks and carefully analyze the performance of the basic RNN model, such as verifying the contribution of sequential information and error rates of different parts of sentences.
 \end{abstract}

### 2013-12-21 paper/paper.tex
Revise abstract further.

@@
 We propose and implement two models: a basic RNN and a Compositional Vector Tagger (CVT) RNN.
-The performance of the basic RNN is close to the HMM model and with high probability will beat it if capitalization information is captured.
+The performance of the basic RNN is close to the HMM model and will likely beat it if capitalization information is captured.
 The intractable tagging time of the CVT model means we cannot analyze it.
-We tried some useful neural network training tricks and carefully analyze the performance of the basic RNN model, such as verifying the contribution of sequential information and error rates of different parts of sentences.
+We tried some useful neural network training tricks and carefully analyze the performance of the basic RNN model, by verifying the contribution of sequential information and error rates of different parts of sentences.
 \end{abstract}

### 2013-12-21 paper/paper.tex
paper: new future work

--- 2013-12-21 paper/paper.tex
@@
 \begin{abstract}
-We use a recursive neural network (RNN) on part-of-speech tagging task (POS).
+ We use recursive neural network (RNN) on part of speech task (POS).
 There are two models are proposed and implemented, basic RNN and Compositional Vector Tagger(CVT) RNN.
@@
 
+\paragraph{Manually Extended Embeddings}
+From the anaysis of Section ~\ref{sec:confm} and also the results in Section ~\ref{sec:modelcomp}, we see that because the disappear of capitalization information of words, the RNN model is bad at telling NN and NNP.
+So we think we can manually extend the embeddings of words by some human made features like captitalized or not, even suffix information.
+This, in our view will definitely improve the performance of model a lot.
+
 \paragraph{Bi-directional Recursive Neural Network}
@@
 So we think a bi-directional model will help, at least compared to the basic RNN.
-As for CVT model, which is simulating the HMM model considering the tags of whole sentence together, a bi-directional model may also help to kind of simulate CRF.
+As for CVG model, which is simulating the HMM model considering the tags of whole sentence together, a bi-directional model may also help to kind of simulate CRF.
 There are two bi-direction models we are thinking:
@@
 
-\paragraph{Rerank with CVT}
-When we implemented and tested the CVT model, the forever tagging time for each sentence stopped us from working with it.
-So in the future, we can use the rerank idea from Socher's CVG paper.
-Basically, we get top N, say 100, tagging candidates from other models, and use CVT model to get score for each sentence and rerank the candidates by these scores.
+\paragraph{Rerank with CVG}
+When we implemented and tested CVG model, the forever tagging time for each sentence stopped us from working with it.
+So in the future, we can use the rerank idea from Socher's SVG paper.
+Basically, we get top N, say 100, tagging candidates from other models, and use CVG model to get score for each sentence and rerank the candidates by these scores.
 
@@
 
-\subsubsection{Comparison to Other Models}
+\subsubsection{Comparison to Other Models}\label{sec:modelcomp}
 
@@
 \begin{itemize}
-\item Training and tagging the CVT model: we have mentioned the hardness of training and tagging with CVT model.
-In the future, we want to training a CVT model no matter how long it may takes, say several days or weeks.
+\item Training and tagging the CVG model: we have mentioned the hardness of training and tagging with CVG model.
+In the future, we want to training a CVG model no matter how long it may takes, say several days or weeks.
 And implement the rerank trick mentioned  in Section \ref{sec:futuremodel}.

### 2013-12-21 paper/paper.tex
Tweaks.

--- 2013-12-21 paper/paper.tex
@@
 But the result was much worse than not updating it.
-But because deep learning researchers do update the feature learning layers (in our model, just lookup table), it is reasonable to try this.
+But because deep learning researchers do update the feature learning layers (in our model, just the lookup table), it is reasonable to try this.
 And instead of updating at the beginning of training, we can begin the updating after other parameters are well trained.
@@
 \item  Another strange confusion is from quotes, which was also met in common HMM models.
-This may come from the overwhelming sequential information, and it makes big difference on accuracy(about 1\% on out-of-domain accuracy), to keep everything trained automatically;
+This may come from the overwhelming sequential information, and it makes a big difference on accuracy (about 1\% on out-of-domain accuracy), to keep everything trained automatically;
 \item Other confusions look normal, and also occur in HMM models, like JJ and NN.

### 2013-12-21 paper/paper.tex
Revision.

--- 2013-12-21 paper/paper.tex
@@
 
+\paragraph{Manually Extended Embeddings}
+From the analysis of Section ~\ref{sec:confm} and also the results in Section ~\ref{sec:modelcomp}, we see that because of the erasure of capitalization information of words, the RNN model is bad at distinguishing between NN and NNP.
+So we think we can manually extend the embeddings of words by some human made features like capitalized or not, or perhaps even suffix information.
+This, in our view, will likely improve the performance of the model a lot.
+
 \paragraph{Bi-directional Recursive Neural Network}

### 2013-12-21 paper/paper.tex

@@
 
-Below, we tally the results against the in-domain validation dataset and the out-of-domain validation dataset on all significantly performing recursive neural network models compared to the hidden-markov-model+TNT, plain hidden-markov-model and maximum likelihood tag models.
+Below, we tally the results against the in-domain validation dataset and the out-of-domain validation dataset on all significantly performing recursive neural network models compared to the hidden-markov-model+TNT, plain hidden-markov-model and maximum likelihood tag model.
 
@@
 
+Also, because we are using fully-trained models, we are certainly overfitting, especially compared to the peak results depicted in Figure \ref{Adagrad_fig}.
+
 \begin{center}
@@
   HMM+TNT & 95.88 & (87.13) & 93.67 & (84.61) \\
-  RNN$_{39815}$ NN=NNP & 94.52 & (88.39) & 91.70 & (83.21) \\
+  AdaGrad RNN$_{10,000}$ NN=NNP & 94.40 & (78.48) & 91.86 & (70.37) \\
+  RNN$_{all}$ NN=NNP & 94.52 & (88.39) & 91.70 & (83.21) \\
   HMM & 95.52 & (63.95) & 91.23 & (53.00) \\
-  AdaGrad RNN$_{39815}$ & 93.58 & (76.90) & 90.41 & (69.82) \\
-  RNN$_{39815}$ & 93.47 & (77.06) & 90.28 & (70.43) \\
+  AdaGrad RNN$_{all}$ & 93.58 & (76.90) & 90.41 & (69.82) \\
+  RNN$_{all}$ & 93.47 & (77.06) & 90.28 & (70.43) \\
   AdaGrad RNN$_{10,000}$ & 93.02 & (79.17) & 90.12 & (73.43) \\
@@
 \section{Conclusion}
+We learned that because we eliminated capitalization information from our training and test data in order to use the distributed word embeddings from Collobert and Weston (2011), we severely handicapped the capability of our model to distinguish a large portion of part-of-speech tags, for instance by confusing proper nouns with regular nouns.
+However, we propose to solve this problem, in order to outperform the hidden-markov-model, by manually extending the word embeddings to encode capitalization, and perhaps plurality.
+
+We also discovered that quotes cause large problems with our model because they frequently occur directly next to nouns, and are thus often confused with nouns.
+We would like to explore manual constraints to resolve this confusion in our model.
+
+We propose to fix the error rate correlated with word index within a sentence by using a bidirectional model to gain context information flowing from both the front and the back of the sentence.
+
+We are looking forward to all the future models proposed and the performance improvements they might bring.
 
@@
 \item Training and tagging the CVT model: we have mentioned the hardness of training and tagging with CVT model.
-In the future, we want to training a CVT model no matter how long it may takes, say several days or weeks.
+In the future, we want to train a CVT model no matter how long it may take, say several days or weeks.
 And implement the rerank trick mentioned in Section \ref{sec:futuremodel}.
 \item Move to GPU: We are working with torch (http://www.torch.ch), which is made by NYU people and supports GPU.
-So in the future, we can use GPU to speed up both traning and tagging.
-And Theano(http://deeplearning.net/software/theano/) can another choice, which has python interface and also GPU supporting and has very good neural networks supporting.
+So in the future, we can use GPU to speed up both training and tagging.
+And Theano (http://deeplearning.net/software/theano/) can be another choice, which has a Python interface and also GPU support and has very good neural network support.
 \end{itemize}
